---
title: "p8105_hw2_gsl2116"
author: "Grace Liu"
date: "9/30/2018"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readxl)
```

## PROBLEM 1
```{r clean_transit, eval=FALSE}
transit_data = read_csv(file = "./HW_Data/NYC_Transit_Subway_Entrance_And_Exit_Data.csv") %>% 
  janitor::clean_names() %>% 
  select(line, station_name, station_latitude, route1:route11, entry, entrance_type, vending, ada) %>% 
  mutate(entry = recode(entry, "YES" = TRUE, "NO" = FALSE))
```
This dataset has 1868 observations and 18 variables (dimensions = 1868 x 18). From the original 32 variables in the dataset, I have only kept 18 that are of interest in my analysis: line, station, name, station latitude / longitude, routes served, entry, vending, entrance type, and ADA compliance. This data set includes character, integer, logical, and numeric variable types.  

#### How many distinct stations are there?
```{r distinct_stations}
nrow(distinct(transit_data, line, station_name))
```
There are `r nrow(distinct(transit_data, line, station_name))` distinct train stations.

#### How many stations are ADA compliant?
```{r ada_stations}
nrow(distinct(filter(transit_data, ada == TRUE), line, station_name))
```
Of these distinct stations, `r nrow(distinct(filter(transit_data, ada == TRUE), transit_data, line, station_name))` are ADA compliant.

#### What proportion of station entrances / exits without vending allow entrance?