---
title: "p8105_hw2_gsl2116"
author: "Grace Liu"
date: "9/30/2018"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readxl)
```

```{r load_data, include=FALSE}
transit_data = read_csv(file = "./HW_Data/NYC_Transit_Subway_Entrance_And_Exit_Data.csv")
  transit_data = janitor::clean_names(transit_data)
  names(transit_data)
```

## PROBLEM 1
```{r clean_transit, results=FALSE}
transit_data = select(transit_data, line, station_name, station_latitude, route1:route11, entry, entrance_type, vending, ada)

recode(transit_data$entry, "YES" = TRUE, "NO" = FALSE)
```

```{r transit_summary, include=FALSE}
skimr::skim(transit_data)
```

This dataset has 1868 observations and 18 variables (dimensions = 1868 x 18). From the original 32 variables in the dataset, I have only kept 18 that are of interest in my analysis: `select(transit_data, line, station_name, station_latitude, route1:route11, entry, entrance_type, vending, ada)`. This data set includes character, integer, logical, and numeric variable types.  

### How many distinct stations are there?
```{r}
distinct()
```


### How many stations are ADA compliant?

### What proportion of station entrances / exits without vending allow entrance?